---
title: "ECON 21020 PSET 3"
author: "Allen Zhou"
date: "10/29/2023"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo = FALSE, include = FALSE}
ds <- read.csv("C:\\Users\\Allen Zhou\\Downloads\\caschool.csv")
library(tidyverse)
library(haven)

```
(a) 420 Observations

(b)
  i. The variable *income* measures the average district income in dollars
  ii. Mean = 15.31659, STD = 7.22589
  iii. Mean = 15316.59, STD = 7225.89. These values are expected as *income* = *avginc* * 1000 so the mean and std should also be 1000 times larger as well
```{r b, echo = TRUE}
ds <- mutate(ds, income = avginc * 1000)

mean_avginc <- mean(ds$avginc)
std_avginc <- sd(ds$avginc)
print(mean_avginc)
print(std_avginc)

mean_income <- mean(ds$income)
std_income <- sd(ds$income)
print(mean_income)
print(std_income)
```

(c)
  i. The mean math score across all districts is
     653.3426
  ii. Fraction of districts = 0.5785714, mean math
      score = 655.7177
  iii. Fraction of districts = 0.4214286, mean math
       score = 650.0819
  iv. Multiplying the fraction with the mean math
      score of each respective districts yields in
      the mean math score across all districts
  v. Let M~s~ be the mean math score for class size
     20 or fewer and let M~l~ be the mean math score 
     for class size larger than 20.
     H~0~: M~s~ = M~l~ or M~s~ - M~l~ = 0
     H~1~: M~s~ != M~l~
     t-statistic: 3.121799
     p-value: 0.001922331
     Since the p-value is less than alpha = 0.1, and
     the t-statistic is greater than the absolute
     value of the critical value, we reject the
     null hypothesis
  vi. Covariance between *avginc* and mean math score
      is 94.7795. Covariance between *income* and
      mean math score is 94779.5. The values are not       the same, but differ by a multiple of 1000,          which makes sense since *income* is *avginc* *
      1000
  vii. Correlation between *avginc* and mean math           score is 0.6993981. Correlation between              *income* and mean math score is also 
       0.6993981. The two correlations are the same         because the two are measuring the same               relationship between average income and mean         math score, the only difference being the            units, which doesn't come into play when             measuring correlation.
```{r c, echo = FALSE}
mean_math <- mean(ds$math_scr)
print(mean_math)

class_size <- filter(ds, str <= 20)
frac1 <- length(class_size$str)/420
print(frac1)

mean_class1 <- mean(class_size$math_scr)
print(mean_class1)

class_large <- filter(ds, str > 20)
frac2 <- length(class_large$str)/420
print(frac2)

mean_class2 <- mean(class_large$math_scr)
print(mean_class2)

print(mean_class1*frac1 + mean_class2*frac2)

ts <- (mean_class1 - mean_class2 -0)/sqrt((sd(class_size$math_scr))^2/length(class_size$math_scr)+(sd(class_large$math_scr))^2/length(class_large$math_scr))
print(ts)

p <- 2 * pt(q = -abs(ts), df = 418)
print(p)

qt(p=0.05, df=418)
t.test(class_size$math_scr, class_large$math_scr)

cov_avgincmath <- cov(ds$avginc, ds$math_scr)
print(cov_avgincmath)
cov_incmath <- cov(ds$income, ds$math_scr)
print(cov_incmath)

corr_avgincmath <- cor(ds$avginc, ds$math_scr)
print(corr_avgincmath)
corr_incmath <- cor(ds$income, ds$math_scr)
print(corr_incmath)
```

```

